Pillar 1 - Sequential Pattern Mining

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
cleaned code

### take / not take, pass / fail / not take
```{r transactions not taken}
d_transactions_not_taken <- expand.grid(

@@

    TNT = case_when(
      is.na(Grade) ~ "not taken",
      TRUE         ~ "taken"
      ),

    TPF = case_when(
      is.na(Grade) ~ "not taken",
      Grade < 5.5  ~ "fail",
      TRUE         ~ "pass"
      ),

    item_TNT = paste(item, TNT, sep = "_"),
    item_TPF = paste(item, TPF, sep = "_")

@@

@@

d_transactions_grade <- d_transactions %>%

@@

  # Gather along rounded grades
  gather(
    key = Grade_round,
    value = "Gr_bool",
    `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, 
    na.rm = TRUE, 
    convert = TRUE
    ) %>%
  select(
    -Gr_bool
    )%>%

@@

@@

#
# Making transactions
transactions     <- make_transaction(item = item   )
transactions_PF  <- make_transaction(item = item_PF)
transactions_HL  <- make_transaction(item = item_HL)
transactions_TNT <- make_transaction(data = d_transactions_not_taken, item = item_TNT)
transactions_TPF <- make_transaction(data = d_transactions_not_taken, item = item_TPF)
transactions_G   <- make_transaction(data = d_transactions_grade    , item = item_G  )

@@

```{r compute_support}
compute_support <- function(AR, data_support, type_rule){

@@

    # include lhs.support
    mutate(
      lhs_course = str_remove_all(lhs, pattern = "_fail|_low|_not taken")
      ) %>%
    left_join(
      select(data_support, item, !!type_rule_enquo),
      by = c("lhs_course" = "item")
      ) %>%
    mutate(
      lhs.support = !!type_rule_enquo
      )  %>%
    select(
      - !!type_rule_enquo
      ) %>%

    # include rhs.support
    mutate(
      rhs_course = str_remove_all(rhs, pattern = "_fail|_low|_not taken")
      ) %>%
    left_join(
      select(data_support, item, !!type_rule_enquo),
      by = c("rhs_course" = "item")
      ) %>%
    mutate(
      rhs.support = !!type_rule_enquo
      ) %>%
    select(
      - !!type_rule_enquo
      )

@@

  data %>%
    my_apriori(appearance = appearance) %>%
    clean_AR %>%
    compute_support(
      data_support = data_support,
      type_rule = !!enquo(type_rule)
      ) %>%
    editing_AR

@@

#
# AR not taken
AR_TNT <- transactions_TNT %>%
  make_AR(

    # impose lhs and rhs to be not taken
    appearance = list(
      both = d_transactions_not_taken %>%
        filter(TNT == "not taken") %>%
        distinct(`item_TNT`) %>%
        pull
    ),

@@

    # impose lhs and rhs to be not taken
    appearance = list(
      rhs = d_transactions_not_taken %>%
        filter(TPF == "fail") %>%
        distinct(`item_TPF`) %>%
        pull
    ),

@@

  # include lhs.support by hand
  separate(
    lhs, 
    into = c("lhs_course", "lhs_grade_round"), 
    sep = "_",
    remove = FALSE,
    convert = TRUE
    ) %>%
  left_join(
    d_support_grade,
    by = c("lhs_course" = "item", "lhs_grade_round" = "grade_round")
    ) %>%
  mutate(
    lhs.support = support.grade
    ) %>%
  select(
    - support.grade
    ) %>%

  # include rhs.support by hand
  separate(
    rhs, 
    into = c("rhs_course", "rhs_grade_round"), 
    sep = "_",
    remove = FALSE,
    convert = TRUE
    ) %>%
  left_join(
    d_support_grade,
    by = c("rhs_course" = "item", "rhs_grade_round" = "grade_round")
    ) %>%
  mutate(
    rhs.support = support.grade
    ) %>%
  select(
    - support.grade
    ) %>%

>>>>

### take / not take, pass / fail / not take
```{r transactions not taken}
d_transactions_TPF <- expand.grid(

@@

    TPF = case_when(
      is.na(Grade)       ~ "not taken",
      Grade < pass_grade ~ "fail",
      TRUE               ~ "pass"
      ),

    item_TPF = paste(item, TPF, sep = "_")

@@

rm(high_grade, pass_grade)
```

@@

d_transactions_G <- d_transactions %>%

@@

  # Gather along rounded grades
  gather(
    key = Grade_round,
    value = X,
    `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, 
    na.rm = TRUE, 
    convert = TRUE
    ) %>%
  select(
    -X
    )%>%

@@

rm(n_students)
```

@@

#
# Making transactions
transactions     <- make_transaction(item = item   )
transactions_PF  <- make_transaction(item = item_PF)
transactions_HL  <- make_transaction(item = item_HL)
transactions_TPF <- make_transaction(data = d_transactions_TPF, item = item_TPF)
transactions_G   <- make_transaction(data = d_transactions_G  , item = item_G  )

@@

```{r compute_support}
compute_metrics <- function(AR, data_support, type_rule){

@@

    # include rhs.support
    mutate(
      rhs_course = str_remove_all(rhs, pattern = "_fail|_low|_not taken")
      ) %>%
    left_join(
      select(data_support, item, !!type_rule_enquo),
      by = c("rhs_course" = "item")
      ) %>%
    mutate(
      rhs.support = !!type_rule_enquo
      )

@@

  data %>%
    my_apriori(appearance = appearance) %>%
    clean_AR %>%
    compute_metrics(
      data_support = data_support,
      type_rule = !!enquo(type_rule)
      ) %>%
    editing_AR

@@

@@

    # impose lhs and rhs to be not taken
    appearance = list(
      rhs = d_transactions_TNT %>%
        filter(TPF == "fail") %>%
        distinct(`item_TPF`) %>%
        pull
    ),

@@

  # include rhs.support by hand
  separate(
    rhs, 
    into = c("item", "grade_round"), 
    sep = "_",
    remove = FALSE,
    convert = TRUE
    ) %>%
  left_join(
    d_support_grade,
    by = c("item", "grade_round")
    ) %>%
  mutate(
    rhs.support = support.grade
    ) %>%
